\documentclass[12pt,letterpaper]{article} % set main text size and page size
% \documentclass[10pt,a4paper]{article}
\usepackage[top=0.4in,bottom=0.4in,left=0.5in,right=0.5in]{geometry} % set page margins
\usepackage{charter} % select font (comment out lines to use Computer Modern)
% \usepackage[default]{lato}
% \usepackage[sfdefault]{carlito}
% \usepackage{tgpagella}
% \usepackage{ebgaramond}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{plex-sans}
% \usepackage{libertine}

% font and input encoding
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem} % enable lists for bullet points: itemize and \item
\usepackage[hidelinks]{hyperref} % format hyperlinks
\usepackage{titlesec} % enable section title customization

% disable text justification
\raggedright

% disable page numbering
\pagestyle{empty}

% ensure that the PDF output will be all unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above/below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above/below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=25pt}

%%%%%%%% resume starts here %%%%%%%%%
\begin{document}

% name
\centerline{\Huge{Richard Leyton-Romero}}

\vspace{5pt} %spacing

% contact information
\centerline{{richieleytongt@outlook.com} | \href{https://www.linkedin.com/in/richieleytongt/}{linkedin.com/in/richieleytongt} | \href{https://github.com/richieleytongt}{github.com/richieleytongt}}

\vspace{-6.5pt} %spacing

%%%%%%% Professional summary %%%%%%%
\section*{Summary}
Controls engineer and PhD researcher specializing in optimal control of nonlinear dynamic systems, with hands-on experience supporting professional motorsport programs.

\vspace{-10.5pt} %spacing

%%%%%%% education section %%%%%%%
\section*{Education}

\textbf{\href{https://www.wits.ac.za/eie/}{University of the Witwatersrand}} -- PhD Electrical Engineering \hfill 2026 \\
\vspace{-9pt}
\begin{itemize}[itemsep=-4pt]
  % \item \textbf{Supervised by:} \href{https://www.nrf.ac.za/about-us/nrf-awards/2022-2/a-rated-researchers-2022/professor-david-j-n-limebeer/}{Professor David J.N. Limebeer}
  \item \textbf{Thesis:} The Use of Optimal Control in the Development of Motorsport Performance
  \begin{itemize}\vspace{-9pt}
    \item Research sponsored by General Motors/Cadillac Formula 1 team.
  \end{itemize}
\end{itemize}

\vspace{-5pt}
\textbf{\href{https://www.brookes.ac.uk/courses/postgraduate/motorsport-engineering-msc}{Oxford Brookes University}} -- MSc Motorsport Engineering \hfill 2023 \\
\vspace{-9pt}
\begin{itemize}[itemsep =-4pt]
    \item \textbf{Dissertation:} The Effects of Race Vehicle Setup on Lap-by-Lap Tire Warm-Up Response
\end{itemize}

\vspace{-5pt}
\textbf{\href{https://www.usf.edu/engineering/me/}{University of South Florida}} -- BSME Mechanical Engineering \hfill 2020 \\
\vspace{-9pt}
% \begin{itemize}[itemsep = -4pt]
%     \item \textbf{Minor:} Entrepreneurship
%     \item \textbf{Senior Design:} Mazda BP4W Camshaft Design
% \end{itemize}

% \vspace{-24.5pt} %spacing

%%%%%%% experience section %%%%%%%

\section*{Experience}
\textbf{Independent Engineering Consultant,} United States \hfill 2019 -- 2023 \\
\vspace{3pt}
\textit{Provided engineering support to organizations such as Pirelli Motorsport, Ian Lacy Racing, Ferrari of North America, Riley Technologies, and Multimatic Motorsports.}
\vspace{-5pt}
\begin{itemize}
  \item Optimized race vehicle setup and stability characteristics through telemetry and driver feedback analysis, improving driver confidence and vehicle consistency.
  \item Used driver-in-the-loop simulation to identify circuit-specific performance limitations and pre-event setup deficiencies, reducing trackside iteration time.
  \item Analyzed tire thermal behavior and wear characteristics during race events to optimize tire usage strategy and maximize performance consistency.
\end{itemize}

\textbf{Engineering Intern,} \href{https://www.compcams.com/}{Comp Cams} -- Memphis, TN \hfill Summer 2019 \\
\vspace{-9pt}
\begin{itemize}
  \item Solved a common Chrysler engine failure by identifying critical point of defect and redesigning hydraulic valvetrain lifter to allow for free flow of oil.
  \item Tuned control parameters for vintage Chevrolet engine retrofitted with modern electronic fuel injection by monitoring and adjusting air:fuel ratios and spark timing.
  \item Provided powertrain consulting for race teams across various motorsport categories from professional drag racing to boat racing.
\end{itemize}

\vspace{-18.5pt} %spacing

%%%%%%% publications section %%%%%%%

\section*{Publications}

Laptime Driven Optimization of Vehicle Suspension Systems (2026). Leyton Romero, R.D., \& Limebeer, D.J.N. \textit{Vehicle System Dynamics}. \href{https://doi.org/10.1080/00423114.2026.2674200}{doi.org/10.1080/00423114.2026.2674200}
\vspace{5pt}

An Optimal Control Approach to the Generation of Yaw-Moment Diagrams (2025). Limebeer, D. J. N., Leyton Romero, R.D., \& Massaro, M. \textit{Vehicle System Dynamics}. \href{https://doi.org/10.1080/00423114.2025.2471344}{doi.org/10.1080/00423114.2025.2471344}

\vspace{-10.5pt} %spacing

%%%%%%% skills section %%%%%%%

\section*{Skills}
\textbf{Scientific Computing:} MATLAB, Julia, Python, Maple, Mathematica \\
% \textbf{Mechanical Design and Simulation:} SOLIDWORKS (certified), CATIA V5, LS-DYNA, STAR-CCM+ \\
\textbf{Motorsport Data Visualization:} MoTeC i2, Cosworth Pi, WinTax4 \\

\vspace{-10.5pt} %spacing

%%%%%% resume ends here %%%%%%%

\end{document}